---
title: "Absolute models"
output: html_document
date: "2022-09-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


**Running environmental predictor analysis with absolute temp ED50s** 

```{r}
#calculate absolute values for each species and reef 
ahum.abs = ahum.1 %>% group_by(Reef) %>% 
  summarise(MMM = mean(MMM)) %>% 
  left_join(emmeans(reef.ahum, ~Reef, param = "e") %>% as.data.frame(), by = "Reef") %>%  
  mutate(absolute = MMM + emmean) %>% 
  mutate(absolute.lowerCL = MMM + lower.CL) %>% 
  mutate(absolute.upperCL = MMM + upper.CL)

pmea.abs = pmea.1%>% group_by(Reef) %>% 
  summarise(MMM = mean(MMM)) %>% 
  left_join(emmeans(reef.pmea, ~Reef, param = "e") %>% as.data.frame(), by = "Reef") %>%  
  mutate(absolute = MMM + emmean) %>% 
  mutate(absolute.lowerCL = MMM + lower.CL) %>% 
  mutate(absolute.upperCL = MMM + upper.CL)

pver.abs = pver.1 %>% group_by(Reef) %>% 
  summarise(MMM = mean(MMM)) %>% 
  left_join(emmeans(reef.pver, ~Reef, param = "e") %>% as.data.frame(), by = "Reef") %>%  
  mutate(absolute = MMM + emmean) %>% 
  mutate(absolute.lowerCL = MMM + lower.CL) %>% 
  mutate(absolute.upperCL = MMM + upper.CL)
```

```{r}
#create a table to easily extract absolute ED50s + CIs for each reef/species combination 
mod.sep.abs = ahum.abs %>% mutate(Species = "A. cf humilis") %>% dplyr::select(Species, Reef, absolute, absolute.lowerCL, absolute.upperCL) %>% 
              bind_rows(pmea.abs %>% mutate(Species = "P. meandrina") %>% dplyr::select(Species, Reef, absolute, absolute.lowerCL, absolute.upperCL)) %>% 
              bind_rows(pver.abs %>% mutate(Species = "P. verrucosa") %>% dplyr::select(Species, Reef, absolute, absolute.lowerCL, absolute.upperCL)) %>% 
    mutate(Reef = factor(Reef, levels(Reef.order)))
```

### Fig 3a_absolute . PSII-50 by reef and species with 95%CI for absolute temperatures 
```{r}
#re-creating figure 3a to visualise differences among reefs and species with absolute ED50s. 
col = wes_palette("GrandBudapest1", 4, type = "continuous")

Fig3a.abs =  ggplot(mod.sep.abs, aes(y = absolute, x = Reef, ymin = absolute.lowerCL, ymax = absolute.upperCL, col = Species)) +
  geom_pointrange(position = position_dodge(width = .4), size = .2) +
  scale_y_continuous(expand = c(0,0), lim = c(5.9,8.5), breaks = c(6.5, 7, 7.5, 8)) +
  scale_colour_manual(values=col) +
  labs(x="Reef", 
       y="ED50 (95% CI)") +
  theme_classic() + 
    scale_y_continuous(expand = c(0,0), limit = c(34,38), breaks = c(34, 35, 36, 37, 38)) + 
  theme(axis.line = element_blank(),
        panel.border = element_rect(size = .5, fill = "transparent"),
        legend.title = element_blank(),
        legend.background = element_rect(fill = "transparent"),
        legend.position = c(.22,.9),
        legend.text = element_text(face = "italic", size = 10, family = "Helvetica"),
        legend.key.size = unit(3, units = "mm"),
        legend.margin = margin(0,0,0,0, unit = "mm"),
        axis.text = element_text(size = 14, family = "Helvetica"),
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title = element_text(size = 14, family = "Helvetica"))

Fig3a.abs
```


```{r}
load("1_data/SiteDisturbanceHistory_DHW.RData")
load("1_data/reef.info.RData")
load("1_data/psii.abs.Rdata")
```

```{r}
#we merge data frames for thermal history metrics and geographic information with the ED50 values 
psii.abs = psii.prediction %>% left_join(mod.sep.abs, by = c("Reef", "Species")) 

#linear relationships
col = wes_palette("GrandBudapest1", 4, type = "continuous")

ggplot(psii.abs, aes(y = absolute, x = value, col = Species, fill = Species)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_fill_manual(values=col) + 
  scale_colour_manual(values=col) +
  labs(y = "ED50", x = "Environmental metric") +
  facet_wrap(~variable, scales = "free") +
  theme_classic() +
  theme(axis.line = element_blank(),
      axis.text.x = element_text(angle = 45, hjust = 1),       
      axis.text = element_text(size = 8, family = "Helvetica"), 
      strip.text = element_text(size = 7)) 

#save(psii.abs, file = "1_data/psii.abs.Rdata")
```



```{r}
#looking at correlation plots for each species against the different environmental metrics. 
psii.abs%>% 
  group_by(variable, Species) %>% 
  summarise(correlation = cor(value, absolute)) %>% 
  ggplot(aes(y = variable, x = Species, fill = correlation)) +
  geom_tile() +
  scale_fill_gradient2(low = "darkred", mid = "white", high = "blue3") +
  theme_classic() + theme(axis.line = element_blank())
```

```{r}
#again looking for variable with relationship > 0.30, but now with absolute temperatures. 
psii.abs %>% 
  group_by(variable) %>% 
  summarise(correlation = cor(value, absolute))
```

```{r}
psii.wide.abs = psii.abs %>% spread(variable, value)
psii.wide.abs
```



We can take a subset of variables to represent the range of climate regimes and have high correlation to ED50 (R > 0.30). Here, we will include 9 environmental variables that represent various regimes. 
```{r}
library(corrplot)
climate.subset.abs = c("Lat", "Long", "maxSST", "meanSST", "maxDHW", "MMM", "recent.maxDHW", "returnDHW6", "returnDHW4")

clim.variables %>% dplyr::select(all_of(climate.subset.abs)) %>% 
  cor()  %>% corrplot() 
#most variables are highly collinear, so we will start by removing some obvious ones: latitude, meanSST, maxSST, maxDHW 
#we want to keep in recent maxDHW (higher correlation) so we remove maxDHW 
#
```

**Here is our selection of the 4 most important variables for describing absolute ED50s that have the lowest collinearity to one another.**  
1. Our priority is to include MMM in the model to ensure that we test the effects of MMM on the absolute temperature ED50. 
2. We must take our highly collinear variables with MMM, so we remove Lat, Long, maxSST, meanSST
3. We select recent.maxDHW and omit maxDHW (collinear)
4. We keep returnDHW6 and returnDHW4 which are not highly collinear with any other variables. 
```{r}
climate.subset.abs2 = c("MMM","recent.maxDHW", "returnDHW6", "returnDHW4")

clim.variables %>% dplyr::select(all_of(climate.subset.abs2)) %>% 
  cor()  %>% corrplot() 
```

**This shows correlation between absolute ED50s and the four environmental variables that will go in the model.**
```{r}
#re-creating the earlier plots with just 4 variables to see the relationship, and any species interactions within the environ. predictors. 
col = wes_palette("GrandBudapest1", 4, type = "continuous")

psii.abs %>% filter(variable %in% climate.subset.abs2) %>% 
  ggplot(aes(y = absolute, x = value, col = Species, fill = Species)) +
  geom_smooth(method = "lm") +
  geom_point() +
  scale_fill_manual(values=col) + 
  scale_colour_manual(values=col) +
  labs(y = "ED50") +
  facet_wrap(~variable, scales = "free") +
  theme_classic() +
  theme(axis.line = element_blank(),
        panel.border = element_rect(size = .5, fill = "transparent"),
        axis.text = element_text(size = 8, family = "Helvetica"),
        axis.title = element_text(size = 9, family = "Helvetica"))
```

## 4.3 Candidate Model Selection 

### Initial dredge
```{r}
#we will use a dredge model that will use an iterative approach to select the model with the lowest AIC value, by putting in the 4 candidate environmental variables. 

library(MuMIn)
library(lme4)
options(na.action = "na.fail")

#creating a data frame with only the 4 variables selected 
dredge.dat.abs1 = psii.abs %>% filter(variable %in% climate.subset.abs2) %>% 
  spread(key = variable, value = value) %>% 
  dplyr::select(-ends_with("CL"), -Reef, -ED50)

#dredge model that accounts for species + the four variables in the model. 
dredge.mod.abs1 <- dredge(lm(absolute~Species +., data = dredge.dat.abs1), rank = "AIC", m.lim = c(1,4))

#just look at the top 10 scoring models 
head(dredge.mod.abs1, 10)

#extracting the best fit model using AIC score 
bestmodel.abs <- get.models(dredge.mod.abs1, 1)[[1]]
lm.dredge1.abs <- lm(bestmodel.abs, data = dredge.dat.abs1)
summary(lm.dredge1.abs)
ggeffects::ggeffect(lm.dredge1.abs) %>% plot
```
*The best model is ED50 ~ MMM + recent.maxDHW + returnDHW6 + Species* 
- This drops out return DHW4 as a variable. 

**We still need to consider the effects of any species interactions. Looking at the plots above, this could be possible for recent.maxDHW or possibly returnDHW6.**

##Dredging with interaction
```{r}
lm.abs1 = lm(absolute~Species + MMM + recent.maxDHW + returnDHW6, data = dredge.dat.abs1)
lm.abs2 = lm(absolute~Species * recent.maxDHW + MMM + returnDHW6, data = dredge.dat.abs1)
lm.abs3 = lm(absolute~Species * returnDHW6 + recent.maxDHW + MMM, data = dredge.dat.abs1)
lm.abs4 = lm(absolute~Species * MMM + returnDHW6 + recent.maxDHW, data = dredge.dat.abs1)
lm.abs5 = lm(absolute~ MMM + returnDHW6 + recent.maxDHW, data = dredge.dat.abs1)


AICc(lm.abs1, lm.abs2, lm.abs3, lm.abs4, lm.abs5)
#model of best fit suggests no interaction between species and any model parameters. 
```
**None of the interactions between species and environmental predictors are significant. 

```{r}
vif(lm.abs1)
```


```{r}
r.squaredGLMM(lm.abs2)
```


```{r}
summary(lm.abs1)
```

